Lessons Learned for JWST Transiting Planet Time Series from Ground-based Studies of the NIRCam Detectors

### 2020-03-06 ms.tex
Updates from Overleaf

\title{Lessons Learned about JWST Transiting Planet Time Series from Ground-based Studies of the NIRCam Detectors}

@@

	\item \textbf{Even/odd offsets:} Alternating columns have different bias levels. Additionally, there are offsets between columns that can change from frame to frame, especially on NIRCam's LW detector.
	These can be reduced with reference pixels or background subtraction.

@@

	This noise would  only become relevant when attempting to make use of the first group of a ramp (such as when only 1 group is commanded).

@@

	JWST's NIRCam instrument has very lower rates of persistence ($<$1 DN/sec) at 100 seconds after saturation, so it is expected that charge trapping will be a minor concern for JWST's HgCdTe detectors.

@@

The thin layer of NIRCam's HgCdTe detector can result in an interference pattern much like thin film interference on bubbles.
Fringing will be less noticeable when many wavelengths are mixed together, but with grism spectra where the wavelengths are separated, the interference effects are more pronounced.
We investigate whether this can manifest itself on the spectrum with the NIRCam grism by looking for periodic signatures that vary in frequency as a function of wavelength.

Figure \ref{fig:cv3ExtractedSpectrum} shows an extracted spectrum from Cryogenic Vacuum 3 testing where a broadband point source is dispersed by the grism.
The slope image is calculated from the raw ramp using the internal NIRCam ramps-to-slopes pipeline \texttt{nchdas}.
The background is subtracted with a 2nd order polynomial fit and the flux is extracted with an optimally weighted summation \citep[e.g.][]{horne1986optimalE}.
The spectrum is normalized by a 3rd order spline fit with 400 knots to remove the broad shape of the spectrum and the throughput curves.
The resulting spectrum shows high frequency ($\sim$0.2 px$^{-1}$ to $\sim$0.5 px$^{-1}$) variations far in excess of the photon and read noise.
These oscillations increase in frequency at longer wavelengths (X pixels).
The variations have peak-to-valley amplitudes of about 10\%.
However, we expect that the fringing structure will hold relatively constant during time so long as the pointing is stable at the sub-pixel level.

\begin{figure}[!hbtp]
\centering
\includegraphics[width=.99\columnwidth]{fringing_grism_cv3.pdf}
\caption{A CV3 grism spectrum over the time series grism test shows evidence for fringing and where the oscillations exceed the photon and read noise (green point).
An illustrative sinusoidal function is plotted for comparison to better see how the frequencies change as a function of wavelength (X pixel).
}\label{fig:CV3GrismSpecFringing}
\end{figure}

@@

\clearpage
\subsubsection{Position of SubGrism Array}

The crosshatch pattern varies in amplitude and angular dependence from one physical location on the detector to another.
The ALONG detector has more pronounced crosshatching toward the middle of the detector that falls off toward the perimeter.
On the other hand, the BLONG detector has more pronounced crosshatching towards the boundary.
We fit the crosshatch pattern to three regions of the ALONG detector, which is the one used for the NIRCam grism time series mode:
\begin{enumerate}
	\item The 2048$\times$64 SUBGRISM position at the bottom of the array where the bottom left corner is (4,5) \label{subgrism64pos}
	\item A 2048$\times$64 theoretical subarray at the top of the ALONG detector where the bottom left corner is (4,1984)
	\item A 2048$\times$64 cutout of the full frame detector that is centered on the grism time series field point.
\end{enumerate}

The three subarrays considered are shown in Figure \ref{fig:subpixScanSimulation}.
We exclude reference pixels (which form a 4 pixel wide boundary around the detector) and an additional row on the bottom and top of the array because these illuminated rows are outliers in the flat field.
The first position is nearly the same as the SUBGRISM64 subarray position in the grism time series mode, except that the SUBGRISM64 includes the first 5 rows which are excluded here from the crosshatch analysis.
The field point used for the SUBGRISM64 mode is expected to be the same one as will be used for the SUBGRISM128 and SUBGRISM256 subarrays.
The position at the top of the ALONG detector has the smallest amplitude of crosshatch pattern in all three directions.
The best-fit amplitudes are used as input to the jitter simulations in Section \ref{sec:CrosshatchSim}.
We find that the maximum flux change for a 0.1 pixel shift is 118 ppm for the nominal grism position, 108 ppm for the top of the array and 153 ppm at the full frame grism position.

@@

Fortunately, the subpixel crosshatch systematic is a smooth function of pointing drift, shown in Figure \ref{fig:subpixScanSimulation}.
A polynomial function can be fit to this subpixel dependence then the centroid of each integration can be inserted as an argument to the function to provide a correction as a function of time.
Alternatively, a Gaussian process regression could be applied.
Centroiding is possible in imaging and spectroscopic modes using PSF fitting or cross-correlation.
When the LW grism time series mode is enabled, SW imaging data will automatically be collected simultaneously enabling the SW centroids to be used to track the motion of the dispersed grism image.
Furthermore, the pixels for time series modes can be characterized in detail because the will be re-used for all time series observations in a given mode.
Target acquisition is expected to achieve centroiding accuracy $\lesssim$ 10 mas ($\lesssim 6$ mas) for unsaturated target acquisition.\footnote{https://jwst-docs.stsci.edu/display/JTI/NIRCam+Time-Series+Imaging+Target+Acquisition}
This ensures that time series observations will reliably return to the same location within the same set of pixels with every visit.

\subsubsection{Time Series Simulation}
The JWST fine steering mirror (FSM) is designed to correct any telescope pointing errors that are not full corrected by the reaction wheels.
The JWST attitude control system team provided a simulation of the expected pointing performance shown in Figure \ref{fig:tserPointingFull}.

The dominant variations in the pointing in the simulation from Figure \ref{fig:tserPointingFull} are High Gain Antenna (HGA) moves.
These are moves are designed to keep the antenna pointing at ground-based antennas for telemetry or data download.
Fortunately, the errors due to HGA moves damp quickly on $\lesssim$ 1 minute e-folding timescales, as show in Figure \ref{fig:tserPointingZoom}.
This means that for 1 minute integrations, only about 1\% of integrations will be affected by HGA moves and the data for these moves could be discarded.
Other pointing errors can be caused by reaction wheel jitter, the MIRI cryocooler and fuel slosh in the fuel tanks.
The effect of the reaction wheels and MIRI cryocooler will be to blur the PSF over an integration since they are higher frequency $\gtrsim 1$ Hz.
Fuel slosh happens at the beginning of a visit after the telescope is slewed, but will dampen quickly on 100 second timescales.
Therefore, the largest contributor to pointing variations will likely be HGA moves and thermal inter-boresight motion.

@@

\begin{figure*}
\gridline{\fig{histos_v2_v3.pdf}{0.45\textwidth}{Pointing Histograms} 
\fig{tser_v2_v3_zoom_none.pdf}{0.45\textwidth}{Pointing Time Series} }
\caption{The typical pointing stability is expected to be extremely stable to within a standard deviation of 2.4 mas (0.04 long wavelength pixels).
This pointing model only shows the line of sight variations, not including thermal distortions or the high frequency ($>$1 Hz) jitter.
}\label{fig:tserPointingFull}
\end{figure*}

@@

We simulate the change in flux as a function of position using our oversampled flat field, as in Figure \ref{fig:subpixScanSimulation}.
First, we bin the sub-pixel jitter time series into 1 minute time bins to represent 1 minute integrations, as shown in Figure \ref{fig:tserPointingAndFlux}.
We then use the positions to shift the PSF on the oversampled flat field as listed at the beginning of this section.
The resulting flux variations are very small compared to factors like the 1/f noise.
The standard deviation of the time series due to small line-of-sight telescope jitter on top of the subpixel crosshatching pattern is only 6 ppm.
Therefore, the line-of-sight subpixel jitter is expected to have a small affect on NIRCam stability.
Furthermore, centroid motion measurements can be used to correct the flux variations due to subpixel jitter with a polynomial or Gaussian process regression.

@@

@@

Table \ref{tab:testSummary} contains a summary of the ground-based tests that were performed on NIRCam detectors.
The flight NIRCam detectors, controllers, electronics, optics and instrument hardware were used in the Cryogenic Vacuum 3 (CV3) Test 3 as well as OTIS (Optical Telescope Element and Integrated Science).
There are also dewars at the Steward Observatory at the University of Arizona used for time series stability tests.
The GL dewar experiments used flight-like detectors, but a different controller (Leach).
The Asic dewar located at Steward Observatory in Tucson, Arizona used the same kind of detectors as NIRCam, the same kind of asic controllers and the same flight software, but no flight-like optics.
These two different kinds of detector electronics can be compared against each other to help isolate optical-related systematics, detector-related systematics and electronics-related systematics.

@@

\begin{deluxetable*}{ccCrlcc}[b!]
\tablecaption{Summary of Ground-Based Tests}\label{tab:testSummary}
\tabletypesize{\footnotesize}
%\tablecolumns{7}
%\tablenum{2}
\tablewidth{0pt}
\tablehead{
\colhead{Name} &
\colhead{Location} &
\colhead{Test Year} &
\colhead{Best Stability} & 
\colhead{Light Source} & 
\colhead{Instrument Mode} &
\colhead{Flight Hardware?} \\
\colhead{} &
\colhead{} &
\colhead{(YYYY)} &
\colhead{(ppm)} &
\colhead{} &
\colhead{} &
\colhead{}
}
\startdata
%Lockheed CV& Lockheed Martin& 2014??    & \nodata   & Darks         & Long Darks & \nodata \\ 
%Reset per int test & Lockheed Martin& 2014??    & \nodata   & Darks         & Long Darks & Y \\ 
CV 3       & NASA Goddard  & 2016       & 500   	& LED           & WLP8 imaging & Y\\
OTIS       & NASA Johnson  & 2017       &   2200    	& Continuum     & Grism spectroscopy & Y\\
OTIS       & NASA Johnson  & 2017       &   21,000    	& Continuum     & WLP8 Imaging & Y \\
GL dewar   & Steward Obs.  & 2015-2016  &       	& LED	        & flood-illuminated imaging & N \\
Asic dewar & Steward Obs.  & 2017-2019  &       	& LED           & pinhole \& flood-illuminated imaging & N\\
\enddata
\tablecomments{Cryogenic vacuum (CV), Optical Telescope element and Integrated Science (OTIS).}
\end{deluxetable*}

@@

The ramps-to-slope pipeline \texttt{ncdhas} or the STScI JWST pipeline will apply reference pixel correction, bad pixels masks and non-linearity correction before fitting the groups up the ramp to a line.
In this work, we use \texttt{ncdhas}.
As seen in Figure \ref{fig:longDarkPhot}, reference pixels can be used to reduce the large offsets between amplifiers.
The reference pixels (making up a 4 pixel boundary on the edges of the detector) are un-illuminated and can therefore be used to measure common-mode electronic noise without being affected by photon counting noise.
The reference pixels are most useful for subtracting the offsets between amplifiers because there are 8 rows of 512 pixels or a total of 4096 reference pixels to average for each amplifier at the bottom and top of the arrays.
There are an additional 4 columns on the left and right side boundaries (8176 pixels) that can be used to further correct the left and right amplifier offests.
However, the 1/f noise that correlates along the fast-read (X) direction is more difficult to remove with reference pixels.
Only 4 pixels on the left and 4 pixels on the right side may be used to subtract the 1/f noise in a given row and the 4 amplifiers can exhibit different 1/f noise. 
Therefore, significantly residuals remain along the fast-read (X) direction in the reference-corrected read pair shown in Figure \ref{fig:longDarkPhot}.
These side reference pixels also cannot give any information about the read noise correlations that happen on shorter length scales than 512 pixels (5 ms).

@@

In our experimental time series, however, the standard deviation in the time series in these 3 apertures is 22,000 to 25,000 DN (without any attempt to correct for 1/f noise using reference pixels or otherwise).
If uncorrected, this extra read noise will contribute 560 to 630 ppm to the time series per read pair!
This read noise would be $\sim$5$\times$ the $\sim$113 ppm photon noise.
Fortunately, there are ways to significantly reduce the 1/f noise.

\begin{deluxetable*}{c|cc|cc}[b!]
\tablecaption{Summary of Noise Sources in OTIS Dark Test}\label{tab:noiseSummary1overf}
\tabletypesize{\footnotesize}
%\tablecolumns{7}
%\tablenum{2}
\tablewidth{0pt}
\tablehead{
\colhead{Aperture} &
\multicolumn{2}{c}{WLP8} &
\multicolumn{2}{c}{Grism 0.17 $\mu$m bin}\\
\colhead{Noise Description} &
\colhead{$\sigma$} &
\colhead{$\sigma$} &
\colhead{$\sigma$} &
\colhead{$\sigma$} \\
\colhead{} &
\colhead{DN} &
\colhead{ppm} &
\colhead{DN} &
\colhead{ppm}\\}
\startdata
Ideal Photon Noise & 4,400 & 113 & 1,520 & 364 \\
Ideal Uncorrelated Read Noise & 1,300 & 33 & 470 & 113 \\
\hline
Measured Read Noise with amplifier offsets (no correction) & 23,500 & 600 & 81,220 & 19,450  \\
Measured Read Noise (reference pixel correction) & 10,800 & 280 & 12,900 & 3,090 \\
Measured Read Noise (reference channel subtraction) & 9,700 & 250 & & \\
Measured Read Noise (row-by-row subtraction) & 6,000 & 150 & 7,120 & 1,705 \\
Measured Read Noise (20 Component PCA subtraction) & 5,400 & 140 & & \\
Measured Read Noise (smoothed 161 px kernel interpolating over aperture) & 3,300 & 85 & & \\
Measured Read Noise (5 Component PCA on each amplifier) & 3,200 & 81 & & \\
Measured Read Noise (row-by-row amp-by-amp mean subtraction) & 2,900 & 75 & & \\
Measured Read Noise (smoothed 40 px kernel on top of aperture) & 900 & 23 & & \\
\enddata
\tablecomments{The theoretical and measured noise sources in one integration for a Weak Lens +8 and Grism Time Series.
The ppm units are assuming a peak 60\% well depth or 3.9$\times 10^7$ DN during an integration for the weak lens PSF and 4.2$\times 10^6$ DN during and integration for the grism PSF.
The noise is the sum within a 70 pixel radius source aperture and 75 to 100 pixel background aperture (in DN) or relative to the photon signal (in ppm).
The integration is assumed to be a bright source with 2 groups of 1 integration each up the ramp (Correlated Double Sampling or CDS mode).}
\end{deluxetable*}

@@

The dramatic difference from the smoothing kernel is beyond what is possible for a real source.
This is because the 40 pixel wide kernel was applied all the way through the source aperture, which would subtract and distort any signal from a star/planet source.
In reality, the kernel should be wider than the source aperture diameter and interpolate through the source points.
Note that this experiment would result in perfect subtraction (0 ppm noise) if the kernel was only 1 pixel wide!
We repeated the experiment with a 161 pixel wide kernel and masked bad pixels and the source pixels.
We use the \texttt{astropy.convolution.convolve()} routine, which calculates a convolution of the kernel by the image.
\texttt{astropy.convolution.convolve()} ignores al NaN values in the mask and renormalizes the kernel by the sum of the remaining kernel points.
This efficiently interpolates over bad pixels and can also interpolate over the source aperture.
Our smoothing kernel is a flat boxcar normalized to 1.0.
This more realistic kernel results in higher noise because of its larger window size and because it interpolates over the aperture points.
The resulting time series has a standard deviation of 2800 DN to 3700 ppm.
This is still larger than the 1,300 DN expectation for uncorrelated read noise, but is below the ideal photon noise limit when integrations reach 60\% well depth.

@@

\subsubsection{Grism Aperture}
The NIRCam grism time series are particularly susceptible to 1/f noise because the dispersion direction is parallel to the detector's fast-read direction.
This is visible in Figure \ref{fig:longDarkGrism} where the grism apertures (in red) are parallel to the 1/f noise correlations.
The background subtraction along the spatial direction (vertically) will efficiently remove pre-amplifier offsets from frame to frame and amplifier to amplifier.
However, there are no side reference pixels or background regions available on the middle two amplifiers.
Therefore, the 1/f noise will adversely impact broadband behaviors of the lightcurves, especially on the middle two amplifiers.

We give some illustrative numbers for a 0.17 $\mu$m wide bin of a grism spectrum as shown in Figure \ref{tab:noiseSummary1overf}.
Without reference pixel subtraction, the grism apertures have standard deviations of 81,200 DN.
Reference pixel subtraction drops this value to 12,900 DN and row-by-row subtraction drops it to 7,120 DN.
For a well depth of 60\%, there are $4.2 \times 10^6$ DN of source counts in the 0.17 $\mu$m bin, which amounts to a photon error of 7,400 DN assuming a gain of 1.84.
Therefore, 1/f noise can potentially dominate the error budget for broadband grism time series!
Expressed in ppm, the read noise after processing with row-by-row subtraction is 90 ppm as compared to a photon noise of 74 ppm for a CDS subtraction (2 groups in ramp).

@@

After experimenting with these configurations, we find the following pipeline steps are important:
\begin{itemize}
	\item Fitting a line up the ramp gives superior results to subtracting the last and first pairs of read (as expected by reducing the read and electronic 1/f noise)
	\item Centering the aperture with the central spot inside the hexagon is important to conserve the flux within the aperture
	\item Row-by-row subtraction (along the detector's fast-read direction) gives superior background subtraction to traditional aperture photometry (using the mean or robust average value in a background annulus)
	\item Aperture sizes for the source at ~70 pixels, outside the hexagon, gave the best precisions
	\item An annulus aperture on the source (including the inner and outer edges of the hexagonal PSF) usually gives the best precision light curves
\end{itemize}

@@

\clearpage
\subsection{OTIS Tests}

@@

\subsubsection{Pass and a Half Grism Time Series Test - Photometry}
The OTIS testing included a time series mode similar to the grism time series template used in orbit for transiting planets.
Figure \ref{fig:otisPSFs} shows the point spread functions for the OTIS tests that simultaneously illuminated the short wavelength and long wavelength channels.
The ``O9'' supercontinuum illuminated the detector over a wide wavelength range from 2.5 to 4.1$\mu$m.
A small fraction of the light is emitted at wavelengths shorter than 2.5 $\mu$m, which is sufficient to illuminate the short wavelength detector to peak counts of $\sim 260$DN per exposure.
Meanwhile, the peak of the grism is $\sim$ 26,000 DN.
This lamp configuration was a pass and a half test, which suffered from the vibrations and oscillations of the suspension system, which can be perturbed by motors such as vacuum pumps.
The telescope is suspended vertically and can potentially swing under these vibrations.

The point spread function through the weak lens and optical setup create a very unusual point spread function for the short wavelength channel, shown in Figure \ref{fig:otisPSFs} that has multiple clumps of emission.
We perform aperture photometry on a knot of emission at (1090 px, 230 px) for the short wavelength detector.
This knot is concentrated enough to fit with a 2D Gaussian and centroid this Gaussian to ~0.2 pixels, which can be used to track the motions of the PSF due to the position oscillations.
For the long wavelength detector, we initially extract a box aperture to create a broadband light curve.

>>>>

\title{Lessons Learned for JWST Transiting Planet Time Series from Ground-based Studies of the NIRCam Detectors}

@@

	\item \textbf{Even/odd offsets:} Alternating columns have different bias levels. Additionally, there are offsets between columns that can change from frame to frame, especially on NIRCam's LW detector

@@

	This noise would  only become relevant when attempting to observe integrations of 1 group up the ramp.

@@

	JWST's NIRCam instrument has very lower rates of persistence (<1 DN/sec) at 100 seconds after saturation, so it is expected that charge trapping will be a minor concern for JWST's HgCdTe detectors.

@@

The thin layer of NIRCam's HgCdTe detector can result in an interference pattern much like thin film interference on bubbles.
We investigate whether this can manifest itself on the spectrum with the NIRCam grism.

\begin{figure}[!hbtp]
\centering
\includegraphics[width=.49\columnwidth]{otis_spec_and_norm.pdf}
\includegraphics[width=.49\columnwidth]{otis_spec_periodogram.pdf}
\caption{The integrated spectrum from Figure \ref{fig:ampOffsetsOtisGrismSlope} shows high frequency noise much far in excess of the spectrum's photon and read noise.
The spectrum is normalized by dividing by a spline fit (bottom left plot) to search for fringing effects
A periodogram shows a peak near 15 pixels period, however, it is not an overwhelming periodic signature.
\textcolor{red}{double check the scatter in spectrum to photon + read noise}
\textcolor{red}{Things to try: 1) keep looking for a fringing in the spectrum. Look at CV3 data, which has a tighter PSF}
}\label{fig:integratedOtisGrismSpec}
\end{figure}

The fringing doesn't show up in the OTIS spectrum from Figure \ref{fig:integratedOtisGrismSpec}, probably because of the broad PSF.
However, the CV3 image in Figure \ref{fig:cv3ExtractedSpectrum} shows a lot of structure in the spectrum.
\textcolor{red}{\bf Is this fringing?}

\begin{figure}[!hbtp]
\centering
\includegraphics[width=.49\columnwidth]{fringing_placeholder.png}
\caption{The CV3 extracted spectrum shows dramatic structure.
Is this fringing?}\label{fig:cv3ExtractedSpectrum}
\end{figure}

@@

@@

Fortunately, the subpixel crosshatch systematic is a smooth function of pointing drift, shown in Figure \ref{fig:subpixScanSimulation}
Smooth functions, such as polynomials, with centroid position will likely 
Centroiding is possible in imaging and spectroscopic modes using PSF fitting or cross-correlation.
When the LW grism time series mode is enabled, SW imaging data will automatically be collected simultaneously enabling the SW centroids to be used to track the motion of the dispersed grism image.
Furthermore, the pixels for time series modes can be characterized in detail because the will be re-used for all time series observations in a given mode.
Target acquisition is expected to achieve centroiding accuracy $\lesssim$ 10 mas ($\lesssim 6$ mas) for unsaturated target acquisition.\footnote{https://jwst-docs.stsci.edu/display/JTI/NIRCam+Time-Series+Imaging+Target+Acquisition}
This ensures that time series observations will reliably return to the same location within the same set of pixels with every visit.

\subsubsection{Time Series Simulation}
The JWST fine steering mirror (FSM) is designed to correct any telescope pointing errors that are not fully corrected by the reaction wheels.
The JWST attitude control system team provided a simulation of the expected ``line of sight'' pointing performance shown in Figure \ref{fig:tserPointingFull}. The line of sight pointing does not include thermal expansion and contraction between instruments that occurs on $\sim$hour long timescales.
The simulation also ignored high frequency ($>$1 Hz) that would blur the PSF but not affect the integration-to-integration time series behavior.
Typical time series integrations are $\sim$ 10 to $\sim$100 seconds in duration.
The transit durations are of order $\sim$1-3 hours.

The dominant variations in the pointing in the simulation from Figure \ref{fig:tserPointingFull} are High Gain Antenna (HGA) moves.
These moves are designed to keep the antenna pointing at ground-based stations for telemetry or data download.
Fortunately, the errors due to High Gain Antenna moves damp quickly on $\lesssim$ 1 minute e-folding timescales.
This means that for 1 minute integrations, only about 1\% of integrations will be affected by HGA moves and the data for these moves could be discarded.
Other pointing errors can be caused by reaction wheel jitter, the MIRI cryocooler and fuel slosh in the fuel tanks.
The effect of the reaction wheels and MIRI cryocooler will be to blur the PSF over an integration since they are higher frequency $\gtrsim 1$ Hz.
Fuel slosh happens at the beginning of a visit after the telescope is slewed, but will dampen quickly on 100 second timescales.
Therefore, the largest contributor to pointing variations will likely be thermal expansion and contraction between JWST instruments.

@@

\begin{figure*}
\gridline{\fig{histos_v2_v3.pdf}{0.45\textwidth}{Pointing Histograms} 
\fig{tser_v2_v3_zoom_none.pdf}{0.45\textwidth}{Pointing Time Series} }
\caption{The line of sight pointing motion is expected to be extremely stable to within a standard deviation of 2.4 mas (0.04 long wavelength pixels).
This pointing model only shows the line of sight variations, not including thermal distortions or the high frequency ($>$1 Hz) jitter.
}\label{fig:tserPointingFull}
\end{figure*}

@@

@@

\subsubsection{Position of SubGrism Array}

The crosshatch pattern varies in amplitude and angular dependence from one physical location on the detector to another.
The ALONG detector has more pronounced crosshatching toward the middle of the detector that falls off toward the perimeter.
On the other hand, the BLONG detector has more pronounced crosshatching towards the boundary.
We fit the crosshatch pattern to three regions of the detector:
\begin{itemize}
	\item The 2048$\times$64 SUBGRISM64 nominal position at the bottom of the array. Bottom Left corner is (0,0)
	\item A 2048$\times$64 theoretical subarray at the top of the ALONG detector. Bottom Left corner is (0,1983)
	\item A 2048$\times$64 cutout of the full frame detector that is centered on the grism time series field point.
\end{itemize}

The three subarrays considered are shown in Figure \ref{fig:subpixScanSimulation}.
The position at the top of the ALONG detector has the smallest amplitude of crosshatch pattern in all three directions.
We exclude reference pixels (which form a 4 pixel wide boundary around the detector) and an additional row on the bottom and top of the array because these illuminated rows are anomalous.
The best-fit amplitudes are used as input to the jitter simulations in Section \ref{sec:CrosshatchSim}.
We find that the maximum flux change for a 0.1 pixel shift is 118 ppm for the nominal grism position, 108 ppm for the top of the array and 153 ppm at the full frame grism position.

@@

Table \ref{tab:testSummary} contains a summary of the ground-based tests that were performed on NIRCam detectors.
The flight NIRCam detectors, controllers, electronics, optics and instrument hardware were used in the Cryogenic Vacuum 3 (CV3) Test 3 as well as OTIS (Optical Telescope Element and Integrated Science).
There are dewars at the Steward Observatory at the University of Arizona used for time series stability tests.
The GL dewar experiments used flight-like detectors, but a different controller (Leach).
The Asic dewar located at Steward Observatory in Tucson, Arizona used the same kind of detectors as NIRCam, the same kind of asic controllers and the same flight software, but no flight-like optics.
These two different kinds of detector electronics can be compared against each other to help isolate optical-related systematics, detector-related systematics and electronics-related systematics.

@@

\begin{deluxetable*}{ccCrlcc}[b!]
\tablecaption{Summary of Ground-Based Tests}\label{tab:testSummary}
\tabletypesize{\footnotesize}
%\tablecolumns{7}
%\tablenum{2}
\tablewidth{0pt}
\tablehead{
\colhead{Name} &
\colhead{Location} &
\colhead{Test Year} &
\colhead{Best Stability} & 
\colhead{Light Source} & 
\colhead{Instrument Mode} &
\colhead{Flight Hardware?} \\
\colhead{} &
\colhead{} &
\colhead{(YYYY)} &
\colhead{(ppm)} &
\colhead{} &
\colhead{} &
\colhead{}
}
\startdata
Lockheed CV& Lockheed Martin& 2014??    & \nodata   & Darks         & Long Darks & \nodata \\ 
Reset per int test & Lockheed Martin& 2014??    & \nodata   & Darks         & Long Darks & Y \\ 
CV 3       & NASA Goddard  & 2016       & 500   	& LED           & WLP8 imaging & Y\\
OTIS       & NASA Johnson  & 2017       &   2200    	& Continuum     & Grism spectroscopy & Y\\
OTIS       & NASA Johnson  & 2017       &   21,000    	& Continuum     & WLP8 Imaging & Y \\
GL dewar   & Steward Obs.  & 2015-2016  &       	& LED	        & flood-illuminated imaging & N \\
Asic dewar & Steward Obs.  & 2017-2019  &       	& LED           & pinhole flood-illuminated imaging & N\\
\enddata
\tablecomments{Cryogenic vacuum (CV), Optical Telescope element and Integrated Science (OTIS).}
\end{deluxetable*}

@@

The ramps-to-slope pipeline \texttt{ncdhas} or the STScI JWST pipeline will apply reference pixel correction, bad pixels masks and non-linearity correction before fitting the groups up the ramp to a line.
In this work, we use \texttt{ncdhas}.
As seen in Figure \ref{fig:longDarkPhot}, reference pixels can be used to reduce the large offsets between amplifiers.
The reference pixels (making up a 4 pixel boundary on the edges of the detector) are un-illuminated and can therefore be used to measure common-mode electronic noise without being affected by photon counting noise.
The reference pixels are most useful for subtracting the offsets between amplifiers because there are 8 rows of 512 pixels or a total of 4096 reference pixels to average for each amplifier at the bottom and top of the arrays.
There are an additional 4 columns on the left and right side boundaries (8176 pixels) that can be used to further correct the left and right amplifier offests.
However, the 1/f noise that correlates along the fast-read (X) direction is more difficult to remove with reference pixels.
Only 4 pixels on the left and 4 pixels on the right side may be used to subtract the 1/f noise in a given row.
Therefore, significantly residuals remain along the fast-read (X) direction in the reference-corrected read pair shown in Figure \ref{fig:longDarkPhot}.
These side reference pixels also cannot give any information about the read noise correlations that happen on shorter length scales than 512 pixels (5 ms).

@@

In our experimental time series, however, the standard deviation in the time series in these 3 apertures is 22,000 to 25,000 DN (without any attempt to correct for 1/f noise using reference pixels or otherwise).
If uncorrected, this extra read noise will contribute 560 to 630 ppm to the time series per read pair!
This would be a very inefficient observations if the read noise dominated the $\sim$113 ppm photon noise.
As can be seen in Figure \ref{fig:longDarkPhot}, there are significant correlations along the fast read (X) direction of the detector due to 1/f noise.

\begin{deluxetable*}{ccc}[b!]
\tablecaption{Summary of Noise Sources in Weak Lens +8 Aperture Dark Test}\label{tab:noiseSummaryWLP8}
\tabletypesize{\footnotesize}
%\tablecolumns{7}
%\tablenum{2}
\tablewidth{0pt}
\tablehead{
\colhead{Noise Description} &
\colhead{$\sigma$} &
\colhead{$\sigma$} \\
\colhead{} &
\colhead{DN} &
\colhead{ppm}\\
}
\startdata
Ideal Photon Noise & 4,400 & 113 \\
Ideal Uncorrelated Read Noise & 1,300 & 33 \\
\hline
Measured Read Noise (no correction) & 23,500 & 600 \\
Measured Read Noise (reference pixel correction) & 10,800 & 280 \\
Measured Read Noise (reference channel subtraction) & 9,700 & 250 \\
Measured Read Noise (row-by-row median subtraction) & 6,000 & 150 \\
Measured Read Noise (20 Component PCA subtraction) & 5,400 & 140 \\
Measured Read Noise (smoothed 161 px kernel interpolating over aperture) & 3,300 & 85 \\
Measured Read Noise (5 Component PCA on each amplifier) & 3,200 & 81 \\
Measured Read Noise (row-by-row amp-by-amp mean subtraction) & 2,900 & 75 \\
Measured Read Noise (smoothed 40 px kernel on top of aperture) & 900 & 23 \\
\enddata
\tablecomments{The theoretical and measured noise sources in one integration for a Weak Lens +8 Time Series.
The ppm units are assuming a peak 60\% well depth or 3.9$\times 10^7$ DN during an integration for the weak lens PSF.
The noise is the sum within a 70 pixel radius source aperture and 75 to 100 pixel background aperture (in DN) or relative to the photon signal (in ppm).
The integration is assumed to be a bright source with 2 groups of 1 integration each up the ramp (Correlated Double Sampling or CDS mode).}
\end{deluxetable*}

@@

The dramatic difference from the smoothing kernel is beyond what is possible for a real source.
This is because the 40 pixel wide kernel was applied all the way through the source aperture, which would subtract and distort any signal from a star/planet source.
In reality, the kernel should be wider than the source aperture diameter and interpolate through the source points.
Note that this experiment with result in perfect subtraction (0 ppm noise) if the kernel was only 1 pixel wide!
We repeated the experiment with a 161 pixel wide kernel and masked bad pixels and the source pixels.
We use the \texttt{astropy.convolution.convolve()} routine, which calculates a convolution of the kernel by the image.
\texttt{astropy.convolution.convolve()} ignores al NaN values in the mask and renormalizes the kernel by the sum of the remaining kernel points.
This efficiently interpolates over bad pixels and can also interpolate over the source aperture.
Our smoothing kernel is a flat boxcar normalized to 1.0.
This more realistic kernel results in higher noise because of its larger window size and because it interpolates over the aperture points.
The resulting time series has a standard deviation of 2800 DN to 3700 ppm.
This is still larger than the 1,300 DN expectation for uncorrelated read noise, but is below the ideal photon noise limit when integrations reach 60\% well depth.

@@

\subsubsection{Grism Aperture}
The NIRCam grism time series are particularly susceptible to 1/f noise because the dispersion direction is parallel to the detector's fast-read direction.
This is visible in Figure \ref{fig:longDarkGrism} where the grism apertures (in red) are parallel to the 1/f noise correlations.
The background subtraction along the spatial direction (vertically) will efficiently remove pre-amplifier offsets from frame to frame and amplifier to amplifier.
However, there are no side reference pixels or background regions available on the middle two amplifiers.
Therefore, the 1/f noise will adversely impact broadband behaviors of the lightcurves.
Without reference pixel subtraction, the grism apertures have standard deviations of 153,000 DN.
Reference pixel subtraction drops this value to 45,000 DN and row-by-row subtraction drops it to 9,000 DN.
For a well depth of 60\%, there are $1.0 \times 10^8$ DN of source counts in an exposure, which amounts to a photon error of 7,400 DN assuming a gain of 1.84.
Therefore, 1/f noise can potentially dominate the error budget for broadband grism time series!
Expressed in ppm, the read noise after processing with row-by-row subtraction is 90 ppm as compared to a photon noise of 74 ppm for a CDS subtraction (2 groups in ramp).

@@

After experimenting with these configurations, we find the following pipeline steps are important:
\begin{itemize}
	\item Fitting a line up the ramp gives superior results to subtracting the last and first pairs of read (as expected by reducing the read noise)
	\item Centering the aperture with the central spot inside the hexagon is important to conserve the flux within the aperture
	\item Row-by-row subtraction (along the detector's fast-read direction) gives superior background subtraction to traditional aperture photometry (using the mean or robust average value in a background annulus)
	\item Aperture sizes for the source at ~70 pixels, outside the hexagon, gave the best precisions
	\item An annulus aperture on the source (including the inner and outer edges of the hexagonal PSF) usually gives the best precision light curves
\end{itemize}

@@

\subsection{OTIS Tests}

@@

\subsubsection{Pass and a Half Grism Time Series Test}
The OTIS testing included a time series mode similar to the grism time series template used in orbit for transiting planets.
Figure \ref{fig:otisPSFs} shows the point spread functions for the OTIS tests that simultaneously illuminated the short wavelength and long wavelength channels.
The ``O9'' supercontinuum illuminated the detector over a wide wavelength range from 2.5 to 4.1$\mu$m.
A small fraction of the light is emitted at wavelengths shorter than 2.5 $\mu$m, which is sufficient to illuminate the short wavelength detector to peak counts of $\sim 260$DN per exposure.
Meanwhile, the peak of the grism is $\sim$ 26,000 DN.
This lamp configuration was a pass and a half test, which suffered from the vibrations and oscillations of the suspension system, which can be perturbed by motors such as vacuum pumps.
The telescope is suspended vertically and can potentially swing under these vibrations.

The point spread function through the weak lens and optical setup create a very unusual point spread function for the short wavelength channel, shown in Figure \ref{fig:otisPSFs} that has multiple clumps of emission.
We perform aperture photometry on a knot of emission at (1090 px, 230 px) for the short wavelength detector.
This knot is concentrated enough to fit with a 2D Gaussian and centroid this Gaussian to ~0.2 pixels, which can be used to track the motions of the PSF due to the oscillations
For the long wavelength detector, we initially extract a box aperture to create a broadband light curve.
